### 2016-02-04 fundamentals/acros.tex
adds neup
adds nrc
Massage the acknoledgements
Reviewer 2: page 18: SWUs please give a complete list of acronyms: here Separate Work Units
advances in engineering software remaining minor comment was to add an s to ton.
Add accent on "Énergie(s)"
Because even if most french do not know how to put accent on
upper case letters, it is not a reason not to do it.

\newacronym{MTHM}{MTHM}{metric ton of heavy metal}

@@

\newacronym{CEA}{CEA}{Commissariat a l'Energie Atomique et aux Energies Alternatives}

@@

@@

>>>>

\newacronym{MTHM}{MTHM}{metric tons of heavy metal}

@@

\newacronym{CEA}{CEA}{Commissariat a l'\'Energie Atomique et aux \'Energies Alternatives}

@@

\newacronym{ThOX}{ThOX}{thorium oxide}

@@

\newacronym{NEUP}{NEUP}{Nuclear Energy University Programs}
\newacronym{NRC}{NRC}{Nuclear Regulatory Commission}
\newacronym{NSF}{NSF}{National Science Foundation}
\newacronym{NNSA}{NNSA}{National Nuclear Security Administration}
\newacronym{DHS}{DHS}{Department of Homeland Security}
\newacronym{SWU}{SWU}{Separative Work Unit}
